Enzo: An Adaptive Mesh Refinement Code for Astrophysics

### 2013-06-12 acknowledgments.tex
acknowledged the people who weren't on the author list.

>>>>

The \enzo\ collaboration would like to acknowledge the following
scientists, who have made contributions to the \enzo\ codebase at some
point during their research career: Brian Crosby, Elizabeth
Harper-Clark, Daegene Koh, Eve Lee, Pascal Paschos, Carolyn Peruta,
Alex Razoumov, Munier Salem, and Rick Wagner.
